\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer (Mobile)} % Job title
    {Aavishkar Technology} % Organization
    {Kathmandu, Nepal} % Location
    {Oct. 2017 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented the Video Streaming Feature on a Linux Based Device for Long Route Buses with an Android App for the bus staffs as the controller}
        \item {Played lead role in developing the core product of the company (FOPI - Video On Demand App) for both Android and iOS.}
        \item {Major areas of work included: Android, Swift, Shell Scripting}
      \end{cvitems}
    }
    
  \cventry
    {Remote Mobile Application Developer} % Job title
    {60 Seconds} % Organization
    {Miranda, New South Wales} % Location
    {Jan. 2020 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed as a remote developer to build a hybrid mobile coaching app using React Native with a simple, clear interface and functionality which encourages practice and private coaching between manager and salesperson.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer (Remote)} % Job title
    {MyriadX - Full Identity Resolution} % Organization
    {Singapore} % Location
    {Sep. 2018 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a patented technology to design and deploy the API for the core product of the company.}
        \item {Contributed as a developer for collection and transformation of data from few of the biggest clients in APAC.}
      \end{cvitems}
    }

  \cventry
    {Remote Developer)} % Job title
    {Converzion Pte. Ltd.} % Organization
    {Boston, MA} % Location
    {Mar. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Involvement in full-stack development in several projects using tools like Angular, Firebase, ExpressJS, Django, Python, Flask, AWS}
      \end{cvitems}
    }

  \cventry
    {Android Tutor/Mentor (Part Time)} % Job title
    {IIT Nepal} % Organization
    {Kathmandu, Nepal} % Location
    {May. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught programming concepts to College students (Kathmandu Bernhardt College, Texas International College) using Java (Android) while providing input for lesson plans and project ideas.}
        \item {Mentored 3rd year student for their Mid-Term Project in Texas International College}
      \end{cvitems}
    }
    
  \cventry
    {President} % Job title
    {Kathford FOSS Community} % Organization
    {Lalitpur, Nepal} % Location
    {2015 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Started a FOSS Community during my College to aware students and colleagues about the importance/advantages of using Free and Open Source Software/Hardware}
        \item {Organized several Competitions, Talks and Seminars as well as mentored students for different projects.}
      \end{cvitems}
    }
\end{cventries}
